Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-14 README.Rmd
removed the flag variable from the training data and add the random forest score to match the test data (now the 14 variables in each data is the same)

`bullet-train`: A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX). XXX Additional information about the number of comparisons.XXX See XXX for additional information on the data. The variables in the data are as follows:

- `r names(bullet_train)[1]` = ID number associated with the bullet-land signature comparison
- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study-barrel number-bullet number-land number'.
- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study-barrel number-bullet number-land number'.
- `r names(bullet_train)[4]`, `r names(bullet_train)[5]`, `r names(bullet_train)[6]`, `r names(bullet_train)[7]`, `r names(bullet_train)[8]`, `r names(bullet_train)[9]`, `r names(bullet_train)[10]`, `r names(bullet_train)[11]`, and `r names(bullet_train)[12]` = comparison features of the two bullet-land signatures. See XXX for definitions of these features.
- `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match
- `r names(bullet_train)[14]` = indictor variable specifying whether one of the bullets in the comparison has tank rash

`bullet-test`: A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX). Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. The first `r dim(bullet_test)[2] - 1` variables in the data are the same as those in the training data (see the variable definitions associated with `bullet-train`). The ``r dim(bullet_test)[2]`th variable is:

- `r names(bullet_test)[14]` = the random forest score associated with the comparison in support of a match

>>>>

`bullet-train`: A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX). This dataset is created using the data available XXX, which contains XXX (add more info about the comparisons). The only changes made to the data from XXX were to remove any lands with tank rash, select only variables of use for the paper, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons. The variables in the data are as follows:

- `r names(bullet_train)[1]` = ID number associated with the bullet-land signature comparison
- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study-barrel number-bullet number-land number'.
- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study-barrel number-bullet number-land number'.
- `r names(bullet_train)[4]`, `r names(bullet_train)[5]`, `r names(bullet_train)[6]`, `r names(bullet_train)[7]`, `r names(bullet_train)[8]`, `r names(bullet_train)[9]`, `r names(bullet_train)[10]`, `r names(bullet_train)[11]`, and `r names(bullet_train)[12]` = comparison features of the two bullet-land signatures. See XXX for definitions of these features.
- `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match
- `r names(bullet_train)[14]` = the random forest score associated with the comparison in support of a match

`bullet-test`: A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX). Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. The `r dim(bullet_test)[2]` variables in the data are the same as those in the training data (see the variable definitions associated with `bullet-train`).

### 2020-09-14 code/data-preparation.Rmd
removed the flag variable from the training data and add the random forest score to match the test data (now the 14 variables in each data is the same)

```{r}
library(cowplot)
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)
```

@@

```{r}
bullet_train <- 
  bullet_train_raw %>%
  filter(flag == FALSE) %>%
  select(-lag, -abs_lag, -overlap, -signature_length) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())
```

>>>>

```{r}
library(cowplot)
library(dplyr)
library(ggplot2)
library(randomForest)
library(stringr)
library(tidyr)
```

@@

```{r}
bullet_train <- 
  bullet_train_raw %>%
  filter(flag == FALSE) %>%
  select(-lag, -abs_lag, -overlap, -signature_length, -flag) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())
```

Add a variable to the training data with the random forest probability in support of a match using the random forest model `rtrees` from `bulletxtrctr`:

```{r}
bullet_features <- rownames(bulletxtrctr::rtrees$importance)
bullet_train$rfscore <- 
  bulletxtrctr::rtrees %>%
  predict(bullet_train %>% select(all_of(bullet_features)), type = "prob") %>%
  data.frame() %>%
  pull(TRUE.)
```
